Selection games and Arhangelskii's convergence principles

### 2019-10-23 articles/selection-alpha-games/article.tex
buncha sequence-like selection game results

It follows that \(\Gamma_X,\Gamma_{X,x}\) are both sequence-like.

@@

\begin{theorem}
Let \(\mc A,\mc B\) be sequence-like. Then \(\alpha_2(\mc A,\mc B)\) holds if and only
if \(\plI\notprewin G_1(\mc A,\mc B)\).
\end{theorem}

@@

Now suppose \(\plI\notprewin G_1(\mc A,\mc B)\). Given \(A_n\in\mc A\) for \(n<\omega\),
first choose \(A_n'=\{a_{n,j}:j<\omega\}\subseteq A_n\) such that \(j<k\) implies
\(a_{n,j}\not=a_{n,k}\),
and then let \(A_{n,m}=\{a_{n,j}:m\leq j<\omega\}\), noting \(A_{n,m}\in\mc A\) since
\(A_{n,m}\) is an infinite subset of \(A_n\in\mc A\). Finally choose
some \(\theta:\omega\to\omega\) such that \(|\theta^{\leftarrow}(n)|=\aleph_0\) for
each \(n<\omega\).

@@

\begin{theorem}
Let \(\mc A,\mc B\) be sequence-like. Then \(\alpha_4(\mc A,\mc B)\) holds if and only
if \(\plI\notprewin G_{<2}(\mc A,\mc B)\) if and only if
\(\plI\notprewin G_{fin}(\mc A,\mc B)\).
\end{theorem}

\begin{proof}
We first assume \(\alpha_4(\mc A,\mc B)\) and let \(A_n\in\mc A\) for \(n<\omega\)
define a predetermined strategy for \(\plI\) in 
\(G_{<2}(\mc A,\mc B)\). We then choose
\(A_n'=\{a_{n,j}:j<\omega\}\subseteq A_n\) such that \(j<k\) implies
\(a_{n,j}\not=a_{n,k}\), and then let \(A_n''=A_n'\setminus\{a_{i,j}:i,j<n\}\),
noting \(A_n''\in\mc A\) since it is an infinite subset of \(A_n\).

@@

>>>>

It follows that \(\Gamma_X,\Gamma_{X,x}\) are both sequence-like. We also require
the following.

\begin{definition}
Say a collection \(\mc A\) is \term{almost-sequence-like} if
for each \(A\in\mc A\), there is \(A'\subseteq A\) such that:
\begin{itemize}
\item \(|A'|=\aleph_0\).
\item If \(A''\) is a cofinite subset of \(A'\), then \(A''\in\mc A\).
\end{itemize}
\end{definition}

So all sequence-like sets are almost-sequence-like.

@@

\begin{theorem}
Let \(\mc A\) be almost-sequence-like and \(\mc B\) be sequence-like. 
Then \(\alpha_2(\mc A,\mc B)\) holds if and only
if \(\plI\notprewin G_1(\mc A,\mc B)\).
\end{theorem}

@@

Now suppose \(\plI\notprewin G_1(\mc A,\mc B)\). Given \(A_n\in\mc A\) for \(n<\omega\),
first choose \(A_n'\in\mc A\) such that \(A_n'=\{a_{n,j}:j<\omega\}\subseteq A_n\),
\(j<k\) implies \(a_{n,j}\not=a_{n,k}\),
and \(A_{n,m}=\{a_{n,j}:m\leq j<\omega\}\in\mc A\).
Finally choose
some \(\theta:\omega\to\omega\) such that \(|\theta^{\leftarrow}(n)|=\aleph_0\) for
each \(n<\omega\).

@@

\begin{theorem}
Let \(\mc A\) be almost-sequence-like and \(\mc B\) be sequence-like. 
Then \(\alpha_4(\mc A,\mc B)\) holds if and only
if \(\plI\notprewin G_{<2}(\mc A,\mc B)\) if and only if
\(\plI\notprewin G_{fin}(\mc A,\mc B)\).
\end{theorem}

\begin{proof}
We first assume \(\alpha_4(\mc A,\mc B)\) and let \(A_n\in\mc A\) for \(n<\omega\)
define a predetermined strategy for \(\plI\) in 
\(G_{<2}(\mc A,\mc B)\). We then may choose \(A_n'\in\mc A\) where
\(A_n'=\{a_{n,j}:j<\omega\}\subseteq A_n\), \(j<k\) implies
\(a_{n,j}\not=a_{n,k}\), and \(A_n''=A_n'\setminus\{a_{i,j}:i,j<n\}\in\mc A\).

@@

\begin{theorem}
Let \(\mc B\) be sequence-like. Then \(\plI\prewin G_{<2}(\mc A,\mc B)\)
if and only if \(\plI\prewin G_{fin}(\mc A,\mc B)\).
\end{theorem}

\begin{proof}
Assume \(\bigcup\mc A\) is well-ordered.
Given a winning predetermined strategy \(A_n\) for \(\plI\) in
\(G_{<2}(\mc A,\mc B)\), consider \(F_n\in[A_n]^{<\aleph_0}\). We set
\[
  F_n^*
=
  \begin{cases}
    \emptyset
      & \text{ if }
    F_n\setminus\bigcup\{F_m:m<n\}=\emptyset
      \\
    \{\min(
      F_n\setminus\bigcup\{F_m:m<n\}
    )\}
      & \text{ otherwise}
  \end{cases}
\]
Since \(|F_n|<2\), we have that \(\bigcup\{F_n^*:n<\omega\}\not\in\mc B\).
In the case that \(\bigcup\{F_n^*:n<\omega\}\) is finite, we immediately
see that \(\bigcup\{F_n:n<\omega\}\) is also finite and therefore not
in \(\mc B\). Otherwise \(\bigcup\{F_n^*:n<\omega\}\not\in\mc B\)
is an infinite subset of \(\bigcup\{F_n:n<\omega\}\), and thus
\(\bigcup\{F_n:n<\omega\}\not\in\mc B\) too. Therefore
\(A_n\) is a winning predetermined strategy for \(\plI\) in
\(G_{fin}(\mc A,\mc B)\) as well.
\end{proof}

\begin{theorem}
Let \(\mc B\) be sequence-like. Then \(\plI\win G_{<2}(\mc A,\mc B)\)
if and only if \(\plI\win G_{fin}(\mc A,\mc B)\).
\end{theorem}

\begin{proof}
Assume \(\bigcup\mc A\) is well-ordered.
Suppose \(\plI\win G_{<2}(\mc A,\mc B)\) is witnessed by the strategy
\(\sigma\). Let \(\tuple{}^\star=\tuple{}\), and for 
\(s\concat\tuple{F}\in([\bigcup\mc A]^{<\aleph_0})^{<\omega}
\setminus\{\tuple{}\}\) let 
\[
  (s\concat\tuple{F})^\star
=
  \begin{cases}
    s^\star\concat\tuple{\emptyset}
      & \text{ if }
    F\setminus\bigcup\ran{s}=\emptyset
      \\
    s^\star\concat\tuple{
      \{\min(F\setminus\bigcup\ran{s})\}
    }
      & \text{ otherwise}
  \end{cases}
\]

We then define the strategy \(\tau\) for \(\plI\) in \(G_{fin}(\mc A,\mc B)\)
by \(\tau(s)=\sigma(s^\star)\). Then given any counterattack
\(\alpha\in([\bigcup\mc A]^{<\aleph_0})^\omega\) by \(\plII\) played against 
\(\tau\), we note that \(\alpha^*=\bigcup\{(\alpha\rest n)^*:n<\omega\}\)
is a counterattack to \(\sigma\), and thus loses.
This means \(B=\bigcup\ran{\alpha^*}\not\in\mc B\).

We consider two cases. The first is the case that \(\bigcup\ran{\alpha^*}\)
is finite. Noting that \(\alpha^*(m)\cap\alpha^*(n)=\emptyset\) whenever
\(m\not=n\), there exists \(N<\omega\) such that 
\(\alpha^*(n)=\emptyset\) for all \(n>N\). As a result,
\(\bigcup\ran{\alpha}=\bigcup\ran{\alpha\rest n}\), and thus
\(\bigcup\ran{\alpha}\) is finite, and therefore not in \(\mc B\).

In the other case, \(\bigcup\ran{\alpha^*}\not\in\mc B\) is an 
infinite subset of \(\bigcup\ran{\alpha}\), and therefore 
\(\bigcup\ran{\alpha}\not\in\mc B\) as well. Thus we have shown
that \(\tau\) is a winning strategy for \(\plI\) in
\(G_{fin}(\mc A,\mc B)\).
\end{proof}

\begin{theorem}
Let \(\mc B\) be sequence-like. Then \(\plII\win G_{<2}(\mc A,\mc B)\)
if and only if \(\plII\win G_{fin}(\mc A,\mc B)\).
\end{theorem}

\begin{theorem}
Let \(\mc B\) be sequence-like. Then \(\plII\markwin G_{<2}(\mc A,\mc B)\)
if and only if \(\plII\markwin G_{fin}(\mc A,\mc B)\).
\end{theorem}

\begin{theorem}\label{pawlikowskii}
Let \(\mc A\) be almost-sequence-like and \(\mc B\) be sequence-like.
Then \(\plI\win G_{fin}(\mc A,\mc B)\) if and only if
\(\plI\prewin G_{fin}(\mc A,\mc B)\).
\end{theorem}

\begin{proof}
We assume \(\plI\win G_{fin}(\mc A,\mc B)\).
As \(\mc A\) is almost-sequence-like, there is a strategy \(\sigma\)
witnessing \(\plI\win G_{fin}(\mc A,\mc B)\) where
\(|\sigma(s)|=\aleph_0\) and \(\sigma(s)\cap\bigcup\ran{s}=\emptyset\)
(that is, \(\sigma\) never replays the choices of \(\plII\))
for all partial plays \(s\) by \(\plII\).

For each \(s\in\omega^{<\omega}\), suppose \(F_{s\rest m}\in[\bigcup A]^{<\aleph_0}\)
is defined for each \(0<m\leq|s|\).
Then let \(s^\star:|s|\to[\bigcup\mc A]^{<\aleph_0}\) be defined by
\(s^\star(m)=F_{s\rest m+1}\), and define \(\tau':\omega^{<\omega}\to\mc A\)
by \(\tau'(s)=\sigma(s^\star)\). Finally, set 
\([\sigma(s^\star)]^{<\aleph_0}=\{F_{s\concat\tuple{n}}:n<\omega\}\), and
for some bijection \(b:\omega^{<\omega}\to\omega\) let \(\tau(n)=\tau'(b(n))\)
be a predetermined strategy for \(\plI\) in \(G_{fin}(\mc A,\mc B)\).

Suppose \(\alpha\) is a counterattack by \(\plII\) against \(\tau\), so 
\[
  \alpha(n)
    \in
  [\tau(n)]^{<\aleph_0}
    =
  [\tau'(b(n))]^{<\aleph_0}
    =
  [\sigma(b(n)^\star)]^{<\aleph_0}
\]
It follows that \(\alpha(n)=F_{b(n)\concat\tuple{m}}\) for some \(m<\omega\).
In particular, there is some infinite subset \(W\subseteq\omega\) and \(f\in\omega^\omega\)
such that \(\{\alpha(n):n\in W\}=\{F_{f\rest n+1}:n<\omega\}\).
Note here that \((f\rest n+1)^\star=(f\rest n)^\star\concat\tuple{F_{f\rest n+1}}\).
This shows that \(F_{f\rest n+1}\in[\sigma((f\rest n)^\star)]^{<\aleph_0}\) 
is an attempt by \(\plII\) to defeat \(\sigma\), which fails. Thus 
\(\bigcup\{F_{f\rest n+1}:n<\omega\}=\bigcup\{\alpha(n):n\in W\}\not\in\mc B\),
and since this set is infinite (as \(\sigma\) prevents \(\plII\)
from repeating choices) we have \(\bigcup\{\alpha(n):n<\omega\}\not\in\mc B\) too.
Therefore \(\tau\) is winning.
\end{proof}

\begin{proposition}\label{auto-asl}
Let \(\mc B\) be sequence-like, \(\mc A\subseteq\mc B\),
and \(\plI\notprewin G_{fin}(\mc A,\mc B)\). Then
\(\mc A\) is almost-sequence-like.
\end{proposition}
\begin{proof}
Let \(A\in\mc A\), and for all \(n<\omega\) let \(A_n=A\).
Then \(A_n\) is not a winning predetermined strategy for
\(\plI\), so \(\plII\) may choose finite subsets
\(B_n\subseteq A_n\) such that \(A_n'\bigcup\{B_n:n<\omega\}\in\mc B\subseteq\mc A\).

It follows that \(|A_n'|=\aleph_0\), and for any infinite subset
\(A_n''\subseteq A_n'\) (in particular, any cofinite subset),
\(A_n''\in\mc B\subseteq\mc A\). Thus \(\mc A\) is almost-sequence-like.
\end{proof}

\begin{corollary}
Let \(\mc B\) be sequence-like and \(\mc A\subseteq\mc B\).
Then \(\plI\win G_{fin}(\mc A,\mc B)\) if and only if
\(\plI\prewin G_{fin}(\mc A,\mc B)\).
\end{corollary}
\begin{proof}
Assuming \(\plI\notprewin G_{fin}(\mc A,\mc B)\), we have
\(\plI\notwin G_{fin}(\mc A,\mc B)\) by Proposition \ref{auto-asl}
and Theorem \ref{pawlikowskii}.
\end{proof}
